Results Summary

### 2025-02-24 results-summary.Rmd

fullResultsForHumans <- fullResults |> 
  mutate(
    estimate_or = estimate_or |> as.numeric(),
    se = se |> as.numeric(),
    t_value = t_value |> as.numeric(),
    p_value = p_value |> as.numeric(),
    lb_95_or = lb_95_or |> as.numeric(),
    ub_95_or = ub_95_or |> as.numeric(),
    method = case_when(
      method == "Naive" ~ "No Adjustment",
      method == "nearest_glm" ~ "Neaset Neighbor Matching, GLM (MatchIt)",
      method == "nearest_gam" ~ "Neaset Neighbor Matching, GAM (MatchIt)",
      method == "nearest_gbm" ~ "Neaset Neighbor Matching, GBM (MatchIt)",
      method == "nearest_lasso" ~ "Neaset Neighbor Matching, LASSO (MatchIt)",
      method == "nearest_mahalanobis" ~ "Neaset Neighbor Matching, Mahalanobis (MatchIt)",
      method == "nearest_rpart" ~ "Neaset Neighbor Matching, Recursive Partinioning (MatchIt)",
      method == "subclass_glm" ~ "Subclassification, GLM (MatchIt)",
      method == "cbps" ~ "IPW, Covariate Balancing Propensity Score (WeightIt)",
      method == "entropy" ~ "IPW, Entropy Balancing (WeightIt)",
      method == "bart" ~ "IPW, Bayesian Additive Regression Trees (WeightIt)",
      method == "twang_gbm" ~ "IPW, GBM (twang)",
      TRUE ~ "Unknown"
    )
  ) |> 
  select(
    method, estimand, estimate_or, se, t_value, p_value, lb_95_or, ub_95_or
  ) |> 
  rename(
    "OR" = estimate_or,
    "SE" = se,
    "t" = t_value,
    "Lower" = lb_95_or,
    "Upper" = ub_95_or
  ) |> 
  arrange(OR) |>
  mutate(method = factor(method, levels = method))

>>>>

fullResultsForHumans <- fullResults |> 
  mutate(
    estimate_or = estimate_or |> as.numeric(),
    se = se |> as.numeric(),
    t_value = t_value |> as.numeric(),
    p_value = p_value |> as.numeric(),
    lb_95_or = lb_95_or |> as.numeric(),
    ub_95_or = ub_95_or |> as.numeric(),
    method = case_when(
      method == "Naive" ~ "No Adjustment",
      method == "nearest_glm" ~ "Nearest Neighbor Matching, GLM (MatchIt)",
      method == "nearest_gam" ~ "Nearest Neighbor Matching, GAM (MatchIt)",
      method == "nearest_gbm" ~ "Nearest Neighbor Matching, GBM (MatchIt)",
      method == "nearest_lasso" ~ "Nearest Neighbor Matching, LASSO (MatchIt)",
      method == "nearest_mahalanobis" ~ "Nearest Neighbor Matching, Mahalanobis (MatchIt)",
      method == "nearest_rpart" ~ "Nearest Neighbor Matching, Recursive Partinioning (MatchIt)",
      method == "subclass_glm" ~ "Subclassification, GLM (MatchIt)",
      method == "cbps" ~ "IPW, Covariate Balancing Propensity Score (WeightIt)",
      method == "entropy" ~ "IPW, Entropy Balancing (WeightIt)",
      method == "bart" ~ "IPW, Bayesian Additive Regression Trees (WeightIt)",
      method == "twang_gbm" ~ "IPW, GBM (twang)",
      TRUE ~ "Unknown"
    )
  ) |> 
  select(
    method, estimand, estimate_or, se, t_value, p_value, lb_95_or, ub_95_or
  ) |> 
  rename(
    "OR" = estimate_or,
    "SE" = se,
    "t" = t_value,
    "Lower" = lb_95_or,
    "Upper" = ub_95_or
  ) |> 
  arrange(OR) |>
  mutate(method = factor(method, levels = method))
